Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-20 paper/paper.tex
updated results section

The paper is organized as follows [\ldots]

\section{Related Work}
General policy and rule-based approaches to dynamic provisioning (e.g. Amazon
Auto Scaling\footnote{\url{http://aws.amazon.com/autoscaling}} and
RightScale\footnote{\url{http://www.rightscale.com}}) allow adjusting the size
of resource pool based on metrics related to infrastructure and application.
Typical infrastructure-specific metric is system load, whereas
application-specific metrics include response time and queue length. It is
possible to set thresholds and limits to tune the behavior of these autoscaling
systems, but no support for complex applications is provided.

@@

\section{Problem Description}

@@

\section{Algorithms}

@@

\section{Performance Evaluation}

@@

\begin{figure}[htb] 
\centering
\includegraphics[width=0.6\columnwidth]{figures/pareto-budget-SIPHT-n-1000-8-dagh5-50h10m0.pdf}
\caption{Comparison of number of workflows completed for a given deadline,
plotted versus different budget amounts.}
\label{fig:budgets}
\end{figure}

@@

\label{tab:num-dags-pareto}
\caption{Number of times each algorithm achieved the highest score 
over all budgets and deadlines. Data from a total of 525 runs on 
Pareto-distributed ensembles for Montage (M), CyberShake (C), LIGO (L), 
Epigenomics (E), SIPHT (S).}
\end{table}

@@

In order to compare efficiency of algorithms, we counted the number of times
each algorithm achieved the best results for all tested applications, deadlines
and budgets. If two or more algorithms achieve the same highest results, all are
counted as highest. Table~\ref{tab:num-dags-pareto} shows these summary values.
These results depend on the metric: number of workflows completed does not count
the priorities or sizes of workflows, which means that it happens more often
that all the algorithms achieve the same (best) result. However, it does not
mean that all algorithms complete the same workflows: that is why values
in the tables (a), (b) and (c) are different. it can be observed that based on
the sampled problem space the workflow-aware algorithms achieve highest score
in $\sim$2--3 times more cases than the simple DPDS which does not take into
account workflow structure or size. In average, SPSS performs better in
$\sim$20--50\% more times than WA-DPDS. We have to note, that the sampled
paramter space included the Montage and CyberShake workflows consisting of many
small tasks, for which cases SPSS does not perform equally well.

Fig.~\ref{fig:budgets} whows the same data for SIPHT ensemble from another
perspective. It helps answer the question: given a deadline, how many workflows
can be finished when we increse the budget. In Fig.~\ref{fig:budgets} the growth
is super-linear, what results from the distribution of workflow sizes in the
ensemble (see Fig.~\ref{fig:ensemble-distribution}). For ensemble of equal size
workflows (see Fig. TODO: ADD FIGURE FROM CONSTANT DISTRIBUTION) the growth is
nearly linear. It can be also observed that staitc algorithms give better
results for smaller budgets, while dynamic algorithms for larger ones.

\section{Conclusion and Future Work}

>>>>

The paper is organized as follows: after analysis of related work in
Section~\ref{sec:related}, Section~\ref{sec:problem} gives the details about the
infrastructure and application model we are targeting in this paper.
Subsequently, in Section~\ref{sec:algorithms} we describe the dynamic and
static algorithms we developed. Section~\ref{sec:performance} presents test
scenarios, metrics and results of simulation studies of these algorithms.
Finally, general conslusions, lessons learned and future work is outlined in
Section~\ref{sec:conclusions}.

\section{Related Work}
\label{sec:related}
General policy and rule-based approaches to dynamic provisioning (e.g. Amazon
Auto Scaling\footnote{\url{http://aws.amazon.com/autoscaling}} and
RightScale\footnote{\url{http://www.rightscale.com}}) allow adjusting the size
of resource pool based on metrics related to infrastructure and application.
Typical infrastructure-specific metric is system load, whereas
application-specific metrics include response time and queue length. It is
possible to set thresholds and limits to tune the behavior of these autoscaling
systems, but no support for complex applications is provided.

@@

\section{Problem Description}
\label{sec:problem}

@@

\section{Algorithms}
\label{sec:algorithms}

@@

\section{Performance Evaluation}
\label{sec:performance}

@@

@@

\caption{Summary table for Pareto-distributed workflows showing number of times
each algorithm achieved the highest score over all budgets and deadlines. Data from a total of 525 runs on 
Pareto-distributed ensembles for Montage (M), CyberShake (C), LIGO (L), 
Epigenomics (E), SIPHT (S).
\label{tab:num-dags-pareto}}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

(a) Number of workflows completed $N_c$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   78 &  93 & 161 &  24  & 30 & 386\tabularnewline
WA-DPDS   &    78  & 97 & 179  & 58  & 28 & 440\tabularnewline
SPSS     &    78  & 79 & 195 &  75 &  50 & 477\tabularnewline
\end{tabular}
\medskip

(b) Total amount of computing time completed $T_C$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   78 &  93 & 161 &  24 &  30 & 386\tabularnewline
WA-DPDS   &    78  & 97 & 179 &  46  & 28 & 428\tabularnewline
SPSS     &    78 &  77 & 195  & 75 &  50 & 475\tabularnewline
\end{tabular}
\medskip

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   78  & 93 & 161 &  24 &  30 & 386\tabularnewline
WA-DPDS   &    78 &  97 & 179  & 46  & 28 & 428\tabularnewline
SPSS     &    78 &  77 & 195 &  75  & 50 & 475\tabularnewline
\end{tabular}
\medskip

\caption{Summary table for equal size workflows whowing number of times each
algorithm achieved the highest score over all budgets and deadlines. Data from a total of 525 runs on 
ensembles of equal size workflows for Montage (M), CyberShake (C), LIGO (L), 
Epigenomics (E), SIPHT (S).
\label{tab:num-dags-equal}}
\end{table}

@@

\begin{figure}[htb] \centering
\includegraphics[width=0.7\columnwidth]{figures/pareto-budget-SIPHT-n-1000-8-dagh5-50h10m0.pdf}\\
(a) ensemble of Pareto-distributed workflows
\includegraphics[width=0.7\columnwidth]{figures/constant-budget-SIPHT-n-1000-0-dagh5-50h4m0.pdf}\\
(b) ensemble of workflows of equal size \caption{Comparison of number of
workflows completed for a given deadline, plotted versus different budget
amounts.}
\label{fig:budgets}
\end{figure}

In order to compare efficiency of algorithms, we counted the number of times
each algorithm achieved the best results for all tested applications, deadlines
and budgets. If two or more algorithms achieve the same highest results, all are
counted as highest. Table~\ref{tab:num-dags-pareto} shows these summary values
for Pareto-distributed workflows. These results depend on the metric: number of
workflows completed does not count the priorities or sizes of workflows, which
means that it happens more often that all the algorithms achieve the same (best)
result. However, it does not mean that all algorithms complete the same
workflows: that is why values in the tables (a), (b) and (c) are different.
Exponential score and total amount of computing time complete give the same
rankings, since in our test ensembles larger workflows were given higher
priorities. It can be observed that based on the sampled problem space the
workflow-aware algorithms achieve highest score in $\sim$2--3 times more cases
than the simple DPDS which does not take into account workflow structure or
size. In average, SPSS performs better in $\sim$20--50\% more times than
WA-DPDS. We have to note, that the sampled paramter space included the Montage
and CyberShake workflows consisting of many small tasks, for which cases SPSS
does not perform equally well.

Similar results were achieved for ensembles consisting of workflows of equal
size. Summary of these results is shown in Table~\ref{tab:num-dags-equal}.
Again, we can see that static SPSS algorithm performed better for coarse-grained
workflows (LIGO, Epigenomics, SIPHT). The differences between algorithm scores
are smaller since the workflows have equal size thus rejecting one workflow
does not help to complete more work in any case.

Fig.~\ref{fig:budgets} shows the same data for SIPHT ensemble from another
perspective. It helps answer the question: given a deadline, how many workflows
can be finished when we increse the budget. In Fig.~\ref{fig:budgets}(a) the
growth is super-linear, what results from the distribution of workflow sizes in
the ensemble (see Fig.~\ref{fig:ensemble-distribution}). For ensemble of equal
size workflows (see Fig.~\ref{fig:budgets}(b)) the growth is nearly linear. It
can be also observed that staitc algorithms give better results for smaller
budgets, while dynamic algorithms for larger ones.

\section{Conclusion and Future Work}
\label{sec:conclusions}
